Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Add more fixes to the paper

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

>>>>

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  we applied the general guidelines described by Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured 
  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

However, we need to take into consideration tickets that have code attachments which are a \emph{thread to validity}. 
When a snippet of code is attached, it might result in more complex tickets due to developers spending more time on 
understanding what is going on and reasoning about the attached code. Also, engineers might need to run or test 
the code attached which can again increase the Time-To-Close.
